---
title: "Cabbages"
author: "Lizeth Marquez"
date: "05/21/2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a data frame called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
$H_0$ There is no difference in average Vitamin C content of cabbages based on cultivation methods (C39,C52)

$H_A$ There is a difference in average Vitamin C content of cabbages based on cultivation method (C39,C52)

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
Vitamin C is numerical, cultivation is categorical

# Results
Numerical~categorical so we use the Numerical~Cat helper file

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
boxplot(VitC~Cult,data=veggy)
```
The box plot shows that cultivation method C52 generally has more Vitamin C than C39 
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
The numerical value shows that C52 gives you more Vitamin C than c39

```{r}
favstats(VitC~Cult,data=veggy)
```
## Inferential Results
```{r}
t.test(VitC~Cult,data=veggy)
```
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question!-->

The p-value 0.0000000034505 < 0.05 was lower, therefore the known null $H_0$ has been rejected. We conclude that the Vitamin C content of cabbages based on cultivation method c39 is less than the Vitamin C cultivation method c52.

# Discussion and Conclusion
The based on the data gathered, the data showed that the Vitamin C content of cabbages of c52 was greater than c39 bit not by much. The known null $H_0$ was been rejected. 
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
